Array Programming with NumPy

### 2020-05-29 _main.tex
Prep for submit process

\documentclass[twocolumn]{wlscirep}

% Packages
\usepackage{moreverb} % for verbatim ouput (for wordcount)
\usepackage{listings, textcomp}
\lstset{language=Python}

\lstset{ %
  basicstyle=\ttfamily\footnotesize,  % size of fonts used for the code
  xleftmargin=\parindent,
  breaklines=true,   % automatic line breaking only at whitespace
  captionpos=b,   % sets the caption-position to bottom
  commentstyle=\color{gray},  % comment style
  keywordstyle=\color{blue},  % keyword style
  stringstyle=\color{red},  % string literal style
  upquote=true  %straight single quotes (requires textcomp)
}

\usepackage[switch]{lineno}
\linenumbers

@@

@@

\keywords{Scientific computing, Python, Mathematics, Array Programming}

\begin{abstract}
\input{summary} 
\end{abstract}

@@

% Count of words
%\verbatiminput{wordcount.tex}

>>>>

\documentclass[twocolumn]{article}

% Packages
\usepackage{textcomp}
\usepackage{graphicx,xcolor}
\bibliographystyle{ieeetr}
%\RequirePackage[superscript,biblabel,nomove]{cite}
%\bibliographystyle{static/naturemag-doi}
%% Automatically abbreviate journal names
%\RequirePackage{jabbrv}
\usepackage{caption}
\RequirePackage[colorlinks=true, allcolors=blue]{hyperref}

\usepackage{titlesec}
\titleformat*{\section}{\large\bfseries}

@@

% Settings for the author block
\RequirePackage{authblk}
\setlength{\affilsep}{1.5em}
\renewcommand\Authfont{\fontsize{12}{12}\usefont{OT1}{phv}{b}{n}}
\renewcommand\Affilfont{\fontsize{8}{10}\usefont{OT1}{phv}{m}{n}}

@@

@@

\twocolumn[
  \begin{@twocolumnfalse}
    \begin{abstract}
    \input{summary} 
    \end{abstract}
    \vspace{1cm}
  \end{@twocolumnfalse}
]
